Vragenlijst thesis evaluatie

### 2015-05-10 doc/template/chap-9.tex
verdere aanvullingen aan deel delay

\section{FlipIt game with virus propagation}
%------------------------------------------------%
%            Intro Game Theory 					 %
%------------------------------------------------%
\subsection{Actions of the attacker}
A virus has different kind of ways of making his way through a company network. We will describe the different ways of how the virus can propagate. For start we will say that the virus or worm will be dropped on Node i and that it has k numbers of neighbours. 
\begin{enumerate}
\item Node i is infected and will spread the virus or worm to every k neighbours and will stop infecting the neighbours in the next step
\item Node i is infected and will spread the virus or worm to every k neighbours and will keep on spreading the virus to the same neighbours in every next step
\item Node i is infected and will spread the virus to only one of the k neighbours and will stop infecting another neighbour in the next step
\item Node i is infected and will spread the virus to only one of the k neighbours and in the next step it will infect another one of the k neighbours 
\end{enumerate}

@@

\subsection{Strategies of both players}
We explained what the actions of each player are.

@@

In this section we provide a formal definition of the game and the notation that we will use throughout the paper. 
\section*{Playing periodically with virus propagation}

@@

\section{Explaining difference between FlipIt with and without virus propagation}
zelfde als in vorige chapter:

>>>>

\section{FlipIt game with virus propagation}

Motivatie voor het veranderen van FLipIt naar een FlipIt met viruspropagatie:

\section{Explaining difference between FlipIt with and without virus propagation}

%------------------------------------------------%
%            Intro Game Theory 					 %
%------------------------------------------------%
\subsection{Actions of the attacker}
A virus has different kind of ways of making his way through a company network. We will describe the different ways of how the virus can propagate. For start we will say that the virus or worm will be dropped on Node i and that it has k numbers of neighbours. 
\begin{enumerate}
\item Node i is infected and will spread the virus or worm to every k neighbours and will stop infecting the neighbours in the next step
\item Node i is infected and will spread the virus or worm to every k neighbours and will keep on spreading the virus to the same neighbours in every next step
\item Node i is infected and will spread the virus to only one of the k neighbours and will stop infecting another neighbour in the next step
\item Node i is infected and will spread the virus to only one of the k neighbours and in the next step it will infect another one of the k neighbours 
\end{enumerate}

@@

@@

In this section we provide a formal definition of the game and the notation that we will use throughout the paper.

\section*{Playing periodically with virus propagation}

@@
